Supplementary Materials

### 2023-07-17 reports/county_figures.Rmd
consistent coloring

@@

county %>% 
  mutate(name=gsub("Nantucket and Dukes", "Nantucket\nand Dukes", name)) %>%
  mutate(vlabel=fct_reorder(vlabel,as.numeric(vlabel),.desc=TRUE)) %>%
   ggplot() +
  geom_ribbon(aes(x = date, 
             ymin = exp_cases_lb,
             ymax = exp_cases_ub),
             alpha = .8,
             show.legend=FALSE,
             fill="#596281") +
  facet_grid(name~vlabel, 
             labeller=labeller(vlabel =as_labeller(
               TeX, default=label_parsed)),
             scales="free") +
  scale_y_continuous(labels = comma) +
  scale_x_date(date_breaks = "3 months", 
               date_labels = "%b %Y") +
  theme_c(
          legend.position = "top",
          ) +
  theme_c(strip.text.x=element_text(size=13,color='white')) +
  scale_fill_manual(values = pal)  +
  labs(x="",
       y = "Estimated Infections",
       title = "Simulation Intervals Over Time",
       subtitle = "Counties in Massachusetts") +
  guides(color = guide_legend(override.aes = list(linewidth =2)))

@@

pal

@@

county_relab %>%
   ggplot() +
  geom_ribbon(aes(x = date, 
             ymin = exp_cases_lb,
             ymax = exp_cases_ub,
             fill=vlabel),
             alpha = .5) +
  facet_wrap(~name,
             scales="free_y") +
  scale_y_continuous(labels = comma) +
  scale_x_date(date_breaks = "3 months", 
               date_labels = "%b %Y") +
  theme_c(
          legend.position = "top",
          legend.text=element_text(hjust=0)
          ) +
  scale_fill_manual(values = pal,
                    labels=TeX(unique(as.character(county_relab$vlabel))))  +
  labs(x="",
       fill="",
       y = "Estimated Infections",
       title = "Simulation Intervals Over Time",
       subtitle = "Counties in Massachusetts") +
  guides(fill=guide_legend(nrow=2))

@@

cat("Maximum ratio, on average, occured: ")
county %>% 
  filter(version=="v7") %>% 
  group_by(biweek) %>% 
  summarize(m = mean(exp_cases_median/positive),dates=paste(range(date),collapse=",")) %>%
  slice_max(n=1, m)

>>>>

convert_labels <- function(labels, to_newlines=TRUE) {

  if(to_newlines) {
    gsub("$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$",
         "$\\overset{Priors\\,Do\\,Not\\,Vary}{\\,by\\,State\\,and\\,Date}$", 
         as.character(labels),
         fixed=TRUE) %>%
    gsub("$P(S_1|untested)$ and $\\beta$ Centered at Survey Values",
         "$\\overset{P(S_1|untested)\\,and\\,beta}{Centered\\,at\\,Survey\\,Values}", 
         .,
         fixed=TRUE)
  }
  else {
      gsub(
         "$\\overset{Priors\\,Do\\,Not\\,Vary}{\\,by\\,State\\,and\\,Date}$", 
         "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$",
         as.character(labels),
         fixed=TRUE) %>%
    gsub("$\\overset{P(S_1|untested)\\,and\\,beta}{Centered\\,at\\,Survey\\,Values}",
         "$P(S_1|untested)$ and $\\beta$ Centered at Survey Values",
         .,
         fixed=TRUE)
  }

@@

names(pal) <- convert_labels(labels(pal), to_newlines=TRUE)

county %>% 
  mutate(name=gsub("Nantucket and Dukes", "Nantucket\nand Dukes", name)) %>%
  mutate(vlabel=fct_reorder(vlabel,as.numeric(vlabel),.desc=TRUE)) %>%
   ggplot() +
  geom_ribbon(aes(x = date, 
             ymin = exp_cases_lb,
             ymax = exp_cases_ub,
             fill = vlabel),
             alpha = .7,
             show.legend=FALSE) +
  facet_grid(name~vlabel, 
             labeller=labeller(vlabel =as_labeller(
               TeX, default=label_parsed)),
             scales="free") +
  scale_y_continuous(labels = comma) +
  scale_x_date(date_breaks = "3 months", 
               date_labels = "%b %Y") +
  theme_c(
          legend.position = "top",
          strip.text.x=element_text(size=13,color='white'),
              axis.title = element_text(size=17),
          plot.title = element_text(size=24, hjust = .5, face="bold", 
                                    margin=margin(2,0,2,0)),
          plot.subtitle = element_text(size=20, face="italic",
                                       margin=margin(1,0,5,0))) +
  scale_fill_manual(values = pal)  +
  labs(x="",
       y = "Estimated Infections",
       title = "Simulation Intervals Over Time",
       subtitle = "Counties in Massachusetts")

@@

# switch labels to version without line breaks for clearer legend
names(pal) <- convert_labels(labels(pal), to_newlines=FALSE)

@@

county_relab %>%
   ggplot() +
  geom_ribbon(aes(x = date, 
             ymin = exp_cases_lb,
             ymax = exp_cases_ub,
             fill=vlabel),
             alpha = .7) +
  facet_wrap(~name,
             scales="free_y") +
  scale_y_continuous(labels = comma) +
  scale_x_date(date_breaks = "3 months", 
               date_labels = "%b %Y") +
  theme_c(
          legend.position = "top",
          legend.text=element_text(hjust=0)
          ) +
  scale_fill_manual(values = pal,
                    labels=TeX(unique(as.character(county_relab$vlabel))))  +
  labs(x="",
       fill="",
       y = "Estimated Infections",
       title = "Simulation Intervals Over Time",
       subtitle = "Counties in Massachusetts") +
  guides(fill=guide_legend(nrow=2))

@@

max_ratio_date <- county %>% 
  filter(version=="v7") %>% 
  group_by(biweek) %>% 
  summarize(m = mean(exp_cases_median/positive),
            dates=paste(range(date),collapse=" to ")) %>%
  slice_max(n=1, m)

cat("Maximum ratio, on average, occured on interval: ",
    max_ratio_date$dates, "on biweek", 
    max_ratio_date$biweek)

### 2023-07-17 reports/state_figures.Rmd
consistent coloring

if(filter_versions){
  state_res <- state_res %>%
  filter(version %in% c("v3", "v5", "v6", "v7"))

@@

subset <- state_res %>%
  filter(vlabel ==  "$\\,$CTIS Priors that Do Not Vary by State or Date$\\,$")

pal <- c("#247C90", "red")

names(pal) <- c(as.character(unique(subset$vlabel)), "Covidestim")

@@

comp_state_pal <- c("#247C90", "red")

names(comp_state_pal) <- c('Probabilistic Bias Analysis', "Covidestim")

@@

state_res %>%
  filter(state == "MI" & version %in% c("v7")) %>%
 # filter(state %in% sample(corrected$state,5)) %>%
  filter(biweek >=6) %>%
  group_by(biweek) %>%
  mutate(xmin = min(date),
         xmax = max(date)) %>%
  ungroup() %>%
   ggplot() +
  geom_ribbon(aes(x = date, 
             ymin = exp_cases_lb,
             ymax = exp_cases_ub),
             fill = "#3E3D3D",
             alpha = .5,
             show.legend=FALSE) +
  # geom_ribbon(aes(x = date,
  #                 fill = 'Covidestim',
  #                 ymin = infections.lo,
  #                 ymax = infections.hi),
  #             alpha = .5) +
  # facet_grid(~vlabel, scales = "free_y",
  #             labeller= labeller(vlabel =as_labeller(TeX, default=label_parsed))) +
  scale_x_date(date_breaks = "2 months", 
               date_labels = "%b %Y") +
  theme_c(legend.position="top") +
  # theme_c(axis.text.x = element_text(size = 16),
  #         axis.title.y = element_text(size=13),
  #         plot.title=element_text(face = "bold",
  #                                 hjust = .5, 
  #                                 size = 24,
  #                                 margin=margin(5,5,15,5,'pt')),
  #         strip.background = element_rect(fill = "#393939"),
  #         strip.text = element_text(color =  "white", size = 16),
  #         strip.text.y = element_text(margin = margin(5,5,5,5,'pt'),
  #                                     size = 22,
  #                                     face="bold"),
  #         strip.text.x =  element_text(margin = margin(5,3,5,3,'pt'),
  #                                      face = "bold",
  #                                      size = 22),
  #         plot.subtitle = ggtext::element_markdown(size = 25,margin = margin(3,5,10,5,'pt'),
  #                                      face = "italic"),
  #         legend.position = "top",
  #         legend.text =element_text(size = 17),
  #         legend.title = element_text(size=18, face="bold")) +
  geom_line(aes(x=week, y=share*m,
                color =variant_category,
                group=variant_category),
            data=variant,
            linewidth=1.3) +
  # scale_fill_manual(values =pal,
  #                   labels = TeX(names(pal)),
  #                    breaks='Covidestim',
  #                   name='')  +
  scale_y_continuous(sec.axis = sec_axis( trans=~./m, name="Variant Proportion"),
                     labels = comma) +
  labs(y = "Estimated Infections",
       title = paste0("Estimated Infections by Version in Michigan"),
       color = "SARS-CoV-2 Variant",
       x="Date") +
  guides(color = guide_legend(override.aes = list(linewidth =3),
                              ncol=2,title.position="top")) +
 # scale_color_brewer(palette="Accent") 
  scale_color_manual(values=varpal)

>>>>

if(filter_versions){
  state_res <- state_res %>%
  filter(version %in% c("v3", "v5", "v6", "v7"))  %>%
    mutate(vlabel=case_when(
      version == "v7" ~  "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$",
      version == "v5" ~ "$\\beta$ Centered at Survey Value",
      version =="v6" ~  "$P(S_1|untested)$ and $\\beta$ Centered at Survey Values",
      version == "v3" ~ "$P(S_1|untested)$ Centered at Survey Value"
    ))

@@

subset <- state_res %>%
  filter(vlabel ==  "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$")

# pal <- c("#247C90", "red")
# 
# names(pal) <- c(as.character(unique(subset$vlabel)), "Covidestim")

@@

# comp_state_pal <- c("#247C90", "red")
# 
# names(comp_state_pal) <- c('Probabilistic Bias Analysis', "Covidestim")
# 
# 
# vlab_for_pal <- unique(subset$vlabel) %>% as.character()

color_for_bias <- pal[[which(names(pal)=="$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$")]]

comp_state_pal<- c(color_for_bias,"red")
names(comp_state_pal) <- c('Probabilistic Bias Analysis', "Covidestim")

@@

state_res %>%
  filter(state == "MI" & version %in% c("v7")) %>%
 # filter(state %in% sample(corrected$state,5)) %>%
  filter(biweek >=6) %>%
  group_by(biweek) %>%
  mutate(xmin = min(date),
         xmax = max(date)) %>%
  ungroup() %>%
   ggplot() +
  geom_ribbon(aes(x = date, 
             ymin = exp_cases_lb,
             ymax = exp_cases_ub,
             fill =vlabel),
           #  fill = "#3E3D3D",
             alpha = .5,
             show.legend=FALSE) +
  # geom_ribbon(aes(x = date,
  #                 fill = 'Covidestim',
  #                 ymin = infections.lo,
  #                 ymax = infections.hi),
  #             alpha = .5) +
  # facet_grid(~vlabel, scales = "free_y",
  #             labeller= labeller(vlabel =as_labeller(TeX, default=label_parsed))) +
  scale_x_date(date_breaks = "2 months", 
               date_labels = "%b %Y") +
  theme_c(legend.position="top") +
  # theme_c(axis.text.x = element_text(size = 16),
  #         axis.title.y = element_text(size=13),
  #         plot.title=element_text(face = "bold",
  #                                 hjust = .5, 
  #                                 size = 24,
  #                                 margin=margin(5,5,15,5,'pt')),
  #         strip.background = element_rect(fill = "#393939"),
  #         strip.text = element_text(color =  "white", size = 16),
  #         strip.text.y = element_text(margin = margin(5,5,5,5,'pt'),
  #                                     size = 22,
  #                                     face="bold"),
  #         strip.text.x =  element_text(margin = margin(5,3,5,3,'pt'),
  #                                      face = "bold",
  #                                      size = 22),
  #         plot.subtitle = ggtext::element_markdown(size = 25,margin = margin(3,5,10,5,'pt'),
  #                                      face = "italic"),
  #         legend.position = "top",
  #         legend.text =element_text(size = 17),
  #         legend.title = element_text(size=18, face="bold")) +
  geom_line(aes(x=week, y=share*m,
                color =variant_category,
                group=variant_category),
            data=variant,
            linewidth=1.3) +
  # scale_fill_manual(values =pal,
  #                   labels = TeX(names(pal)),
  #                    breaks='Covidestim',
  #                   name='')  +
  scale_y_continuous(sec.axis = sec_axis( trans=~./m, name="Variant Proportion"),
                     labels = comma) +
  labs(y = "Estimated Infections",
       title = paste0("Estimated Infections by Version in Michigan"),
       color = "SARS-CoV-2 Variant",
       x="Date") +
  guides(color = guide_legend(override.aes = list(linewidth =3),
                              ncol=2,title.position="top")) +
 # scale_color_brewer(palette="Accent") 
  scale_color_manual(values=varpal) +
  scale_fill_manual(values=pal)

### 2023-07-17 writing/supplement.Rmd
consistent coloring

>>>>

```{r sim-intervals-faceted-county, fig.width=15, fig.height=16,  fig.cap = "Simulation intervals for counties in Massachusetts. Each interval corresponds to a 95\\% simulation interval for the total number of estimated infections for that county in that two-week time interval. The columns represent different implementations of the probabilistic bias analysis: in the first through the third columns, the priors vary by state and date, while for the fourth, they are the same for all states and time intervals considered. For the implementation in the first column, we center the distribution of $\\beta$ at the ratio of the screening test positivity to the overall test positivity from the survey, and we center the distribution of $\\Pr(S_1|\\text{untested})$ at the percentage of the population experiencing COVID-19-like illness from the survey for each two-week interval. The second column centers only $\\beta$ at the aformentioned value, and the third column only centers $\\Pr(S_1|\\text{untested})$ at the aforementioned value. The fourth column corresponds to the implementation where we specify priors that are the same for all dates. The implementation that centers both $\\Pr(S_1|\\text{untested})$ and $\\beta$ at the survey values is consistently the highest among the implementations, followed by the implementation that centers only $\\beta$ at the survey value, followed then by the implementation only centering $\\Pr(S_1|\\text{untested})$ at the survey value, and then the lowest among the implementations is that where the priors do not vary by date."}

include_graphics(here('figures/simulation-intervals-faceted-version-county.pdf'))
